
Question #1
-----------

A random sample of size 10 was taken form a normal population. If the observations are 65,71,64,71,70,69,64,63,67, and 68, test the hypothesis that the population mean is 69 inches. Also obtain 99% confidence interval for the population mean

```{r}
dat=c(67,71,64,71,70,69,64,63,67,68)
t.test(dat,mu=69)
```
We accept the null hypothesis since the t value falls under the confidence interval
```{r}
t.test(dat,mu=69,conf.level = .99)
```

#Function to find the zvalue#

```{r}
zvalue = function(x,myu,psigma=NULL,ssigma=NULL,n)
{
  if(missing(psigma))
  {
    no=sqrt(n)
    z=(x-myu)/(ssigma/no)
    return(z)
  }
  else
  {
    no=sqrt(n)
    z=(x-myu)/(psigma/no)
    return(z)
  }
}
```

#function to find the SNT values#
```{r}
zsig=function(sig.level,tail1=c("One","Two"))
{
  if("One" %in% tail1)
  {
    return(abs(qnorm(sig.level)))
  }
  else
  {
    return(abs(qnorm(sig.level/2)))
  }
  
}
```

#Function to find the ztable values according to the tail#

```{r}
ztail=function(sig.level,tail2=c("L","R","T"))
{
  if("L" %in% tail2)
  {
    t1=-(zsig(sig.level))
    return(t1)
  }
  else if("R" %in% tail2)
  {
    t1=(zsig(sig.level))
    return(t1) 
  }
  else
  {
    t1=-(zsig(sig.level,2))
    t2=(zsig(sig.level,2))
    return(c(t1,t2))
  }
}
```


#Function to find x>myu#

```{r}
zleft=function(z1,z2)
{
if(z1>z2)
  print("Accept Null Hypothesis")
else
  print("Reject Null Hypothesis, and accept Alternative hypothesis")
}

```


#Function to find x!=myu#
--------------------------

```{r}
ztwo=function(z1,z2)
{
  if(z1>z2[1] && z1<z2[2])
  {
    print("Accept Null Hypothesis")
  }
  else
  {
    print("Reject null hypothesis, and accept alternative hypothesis")
  }
}
```

Question #2
-------------

A machine part was designed to withstand an average pressure of 120 units. A random sample of size 100 from a large batch was tested and it was found that the average pressure which these parts can withstand is 105 units with a standard deviation of 20 units. Test whether the batch meets the specifications

Null Hypothesis : x=120
Alternate Hypothesis : x>120

#Arguments of Zvalue are , x=sample mean,myu=population mean,psigma=population standard deviation,ssigma=Sample standard deviation,n=sample size#

```{r}
z1=zvalue(x=105,myu=120,ssigma = 20,n=100)
z1
```
#Arguments of Ztail are , sig.level=Significance level , tail2= "Left" or "Right" or "Two" tailed

```{r}
z2=ztail(sig.level = 0.05,tail2 = "L")
z2
```

#Arguments for zleft are , z1=zvalue from the data , z2=zvalue from the table

```{r}
zleft(z1,z2)
```

Question #3
------------

A sample of 400 male students is found to have a mean height 171.38 cms. Can it be reasonably regarded as a sample from a large population with mean height 171.7cms and s.d 3.30

Null Hypothesis : x=171.7
Alternate Hypothesis : x !=120

```{r}

z3=zvalue(x=171.38,myu=171.7,psigma = 3.30,n=400)
z3
```

```{r}
z4=ztail(sig.level = .05,tail2="T")
z4
```

```{r}
ztwo(z3,z4)
```

Question #4
-------------

Ten oil tins taken at random from an automatic filling machine shows that mean weight of tin is 16.52 kg with a standard deviation of .5kg. Does the sample mean differ significantly from the standard weight of 17kg

Null Hypothesis : x=17kg
Alternate Hypothesis : x!=17

```{r}
z5=zvalue(x=16.52,myu=17,ssigma = .5,n=10)
z5
```

```{r}
z6=ztail(sig.level = .05,tail="T")
z6
```

```{r}
ztwo(z5,z6)
```
